% !TEX root = main.tex

As I embark on the task of acknowledging those whose support and inspiration have been instrumental in the creation of this workbook, I find myself deeply grateful to the remarkable individuals who have shaped my journey in mathematics education.

First and foremost, I express my heartfelt gratitude to my wife, whose unwavering support, encouragement, and patience have been my constant pillars. Her belief in my work and her boundless love have provided me with the strength to undertake this endeavor. To my daughters, who have brought immense joy and laughter into our lives, thank you for your understanding during the long hours spent crafting these pages. Your presence has been my source of inspiration, reminding me of the importance of education for future generations.

I extend my sincere appreciation to my teachers, whose passion for teaching ignited the spark of curiosity within me. Their dedication to nurturing young minds has been a guiding light, and I am forever indebted for their wisdom and guidance. It is through their teachings that I found my love for mathematics, a passion I aim to instill in others through this workbook.

To my previous students, your enthusiasm, questions, and thirst for knowledge have been the driving force behind this project. Your engagement in the classroom has challenged me to find innovative ways to explain complex concepts, and your success stories continue to inspire me. Each interaction with you has reinforced my belief in the transformative power of education.

I am also grateful for the support and encouragement I have received from colleagues, friends, and mentors. Your insights and discussions have enriched my understanding of calculus and teaching methodologies, shaping the content of this workbook.

Lastly, I extend my thanks to the countless authors, researchers, and educators whose contributions to the field of mathematics have paved the way for innovative teaching approaches. Your work has been a wellspring of knowledge and ideas, shaping the content of this workbook and enriching the learning experience for readers.

To all of you, I offer my deepest gratitude. This workbook stands as a testament to the collective effort and shared passion for education. May it serve as a valuable resource for learners, igniting the same love for calculus that has been kindled in me by the remarkable individuals in my life.

\vspace{1cm}
\noindent With heartfelt appreciation,

\noindent Rizauddin Saian\\
\noindent \date{8 Oct 2023}